---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Computational Reproducibility in Archaeological Research: Basic Principles and a Case Study of Their Implementation

### Compendium URL

https://dx.doi.org/10.6084/m9.figshare.1563661

### Author

Ben Marwick (benmarwick@gmail.com)

### Contents

This repository contains the research compendium for my paper in the _Journal of Archaeological Method and Theory_:

> Marwick, B. (2016). Computational reproducibility in archaeological research: Basic principles and a case study of their implementation. _Journal of Archaeological Method and Theory_, 1-27. doi: 10.1007/s10816-015-9272-9


The paper is available as a free [PDF](https://github.com/benmarwick/basic_computational_reproducibility_case_study/raw/master/published/Marwick_2016_basic_computational_reproducibility.pdf), an [Open Access author-accepted manuscript], or on the subscription-only site for the [Journal of Archaeological Method and Theory](http://link.springer.com/article/10.1007/s10816-015-9272-9)

Here's a bibtex-style citation for easy copy-pasting:

```
@article{
year={2016},
issn={1072-5369},
journal={Journal of Archaeological Method and Theory},
doi={10.1007/s10816-015-9272-9},
title={Computational Reproducibility in Archaeological Research: Basic Principles and a Case Study of Their Implementation},
url={http://dx.doi.org/10.1007/s10816-015-9272-9},
publisher={Springer US},
keywords={Reproducible research; Computer programming; Software engineering; Australian archaeology; Open science},
author={Marwick, Ben},
pages={1-27},
language={English}
}
```


### How to use

See the [`text`](https://github.com/benmarwick/basic_computational_reproducibility_case_study/tree/master/text) directory on GitHub for the [source code](https://github.com/benmarwick/basic_computational_reproducibility_case_study/blob/master/text/basic_computational_reproducibility.Rmd) that generated the manuscript. The Rmd file is the original source document, and the docx file was required by the publisher for submission. 

See the published PDF ([view in browser](https://github.com/benmarwick/basic_computational_reproducibility_case_study/blob/master/published/Marwick_2016_basic_computational_reproducibility.pdf) or [download](https://github.com/benmarwick/basic_computational_reproducibility_case_study/raw/master/published/Marwick_2016_basic_computational_reproducibility.pdf))(https://github.com/benmarwick/basic_computational_reproducibility_case_study/tree/master/published) here in this repository. 

### Dependencies

I used [RStudio](http://rstudio.com/) v0.99.825 with [Pandoc](http://pandoc.org/) 1.13.2. To generate a docx from the Rmd, see the `R Session Information` below for the R version and packages that I used. To generate a PDF, I used LaTeX ([MiKTeX](http://miktex.org/) 2.9). 

### Licenses:

Text: CC-BY-4.0 http://creativecommons.org/licenses/by/4.0/

Code: MIT http://opensource.org/licenses/MIT year: 2015, copyright holder: Ben Marwick

Data: CC0 http://creativecommons.org/publicdomain/zero/1.0/ 


### Notes and resources ##

* The [issues tracker](https://github.com/benmarwick/basic_computational_reproducibility_case_study/issues) is the place to report problems or ask questions  

* See the repository [history](https://github.com/benmarwick/basic_computational_reproducibility_case_study/commits/master) for a fine-grained view of progress and changes.

* The organisation of this compendium is based on the work of [Carl Boettiger](http://www.carlboettiger.info/) 

### R Session Information

````{r}
sessionInfo()
```
