---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Computational Reproducibility in Archaeological Research: Basic Principles and a Case Study of Their Implementation

### Compendium URL

https://dx.doi.org/10.6084/m9.figshare.1563661

### Author

Ben Marwick (benmarwick@gmail.com)

### Contents

This repository contains the research compendium for my paper in the _Journal of Archaeological Method and Theory_:

> Marwick, B. (2016). Computational reproducibility in archaeological research: Basic principles and a case study of their implementation. _Journal of Archaeological Method and Theory_, 1-27. doi: 10.1007/s10816-015-9272-9


The paper is available as an Open Access author-accepted manuscript, or the final published copy on the subscription-only site for the [Journal of Human Evolution](http://link.springer.com/article/10.1007/s10816-015-9272-9)

Here's a bibtex-style citation for easy copy-pasting:

@article{
year={2016},
issn={1072-5369},
journal={Journal of Archaeological Method and Theory},
doi={10.1007/s10816-015-9272-9},
title={Computational Reproducibility in Archaeological Research: Basic Principles and a Case Study of Their Implementation},
url={http://dx.doi.org/10.1007/s10816-015-9272-9},
publisher={Springer US},
keywords={Reproducible research; Computer programming; Software engineering; Australian archaeology; Open science},
author={Marwick, Ben},
pages={1-27},
language={English}
}


### How to use

See the [`text`](https://github.com/benmarwick/basic_computational_reproducibility_case_study/text) directory on GitHub for the source code that generated the manuscript. The Rmd file is the original source document, and the docx was required by the publisher for submission. 

See the [`published PDF`](https://github.com/benmarwick/basic_computational_reproducibility_case_study/published) here in this repository. 

### Dependencies

I used RStudio v0.99.825. To generate a docx from the Rmd, see the `R Session Information` below for the R version and packages that I used. To generate a PDF, I used LaTeX (MiKTeX 2.9). 

### Licenses:

Text: CC-BY-4.0 http://creativecommons.org/licenses/by/4.0/

Code: MIT http://opensource.org/licenses/MIT year: 2015, copyright holder: Ben Marwick

Data: CC0 http://creativecommons.org/publicdomain/zero/1.0/ 


### Notes and resources ##

* The [issues tracker](https://github.com/benmarwick/basic_computational_reproducibility_case_study/issues) is the place to report problems or ask questions  

* See the repository [history](https://github.com/benmarwick/basic_computational_reproducibility_case_study/commits/master) for a fine-grained view of progress and changes.

* The organisation of this compendium is based on the work of [Carl Boettiger](http://www.carlboettiger.info/) 

### R Session Information

````{r}
sessionInfo()
```
